### 2024-04-17 texts/paper_closing.tex
paper update: new org version? wcpF, add limitation note

% Created 2024-04-07 zo 17:21
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

\setlength{\parindent}{1.2cm}
\author{Johannes Aengenheyster}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Johannes Aengenheyster},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 29.2 (Org mode 9.6.21)}, 
 pdflang={English}}
\begin{document}

\section*{Identity and the closure of private art museums}
\label{sec:org16a7685}

\subsection*{Introduction}
\label{sec:orgef6a080}

@@

\subsection*{Theoretical framework}
\label{sec:org90170ed}

@@

\subsubsection*{Identity and the survival prospects of non-profit organizations}
\label{sec:org8725d02}
An identity that is legitimate (understandable) and favorable (positive) has been shown to have a vast number of positive outcomes for organizations \parencite{Lange_Lee_Dai_2010_reputation}.
As gaining the approval of different stakeholders is necessary for being understood and/or supported by other organizations in the environment, having a clearly defined and favorable identity influences resource acquisition and thereby survival prospects \parencite{Rao_1994_reputation}.
Even for non-profit organizations such as museums, which do not produce tangible goods (a domain where identity-related effects are present, e.g. \cite{Hsu_2015_granted,Bogaert_etal_2014_ecological}), a clear and positive identity might be helpful in a number of ways:
In particular in the context of private museums, decline of legitimacy or reputation could lead to lower visitor numbers, less discounts from art dealers, less government grants or lower chances on collaborations with other museums or corporations, resulting in lower revenues and higher acquisition costs.

@@

\subsubsection*{Organizational transformation}
\label{sec:org19d4baf}
\textcite{Carroll_Khessina_2019_demography} argue that transformation of core features of organizations such as changes in technology or authority can have divergent consequences. 
On the one hand, it can disrupt internal routines as well as external customer relations by decreasing (perceived) reliability and accountability as the change upsets established perceptions, which can lead to higher mortality. 
On the other hand, organizational transformation can be necessary to adapt to a changing environment, and hence be beneficial for survival.

@@

\subsubsection*{Competition}
\label{sec:org9840956}

@@

\subsubsection*{Other predictors of organizational survival}
\label{sec:org9672c62}
\paragraph*{Age}
\label{sec:orgae2e32a}

@@

\subsection*{Data and Methods}
\label{sec:org6923afe}

\subsubsection*{Dependent Variable}
\label{sec:org7efae3c}
A newly constructed database, assembled from different sources,  is used to measure the survival of private museums (cf. \textcite{Velthuis_etal_2023_boom} for details).
First, existing databases of private art museums are harmonized.
Secondly, the online presences of 14 English art publications were exhaustively searched for any mention of private museums.
After identifying unique institutions, data on these organizations was collected such as opening year, closing year (of those which closed) and founder information.
Currently, the database includes 547 museums (of which 446 are currently open, the remainder having closed or transformed into other organizational forms).
Using this database allows to reconstruct the lifecourse of the each institution with the the unit of analysis as museum-year:
The main dependenent variable is thus an indicator of museum closure, which takes the value of 1 for the museums which close in the year of their closure, and 0 otherwise.
Typically for survival data, museums that do not close during the observation period are right-censored, i.e. for such museums the dependent variable is zero for all years.

\subsubsection*{Main Predictors}
\label{sec:orge0e80eb}

\paragraph*{Legitimacy}
\label{sec:org9952eec}

@@

\paragraph*{Reputation}
\label{sec:org051c5db}

@@

\paragraph*{Organizational transformation}
\label{sec:org671fa45}
A measure of founder death is constructed as a time-varying covariate, and is set to 1 for museum-years after the death of the founder.

\paragraph*{Competition}
\label{sec:orgc059910}
On a national level, density of private museum is calculated as the number of private museums per million.
On a local level, I use the Global Human Settlement Layer \parencite{EC_2023_GHSL} to estimate the number of private museums and population counts inside a radius of ten kilometers around each private museum for each year.
To be able to estimate both competition and demand/audience/population separately, I do not calculate densities as per capita rates, but include the local museum counts, local population in millions as well as an interaction between the two.

\subsubsection*{Control variables}
\label{sec:org4412539}

@@

\subsubsection*{Analytical framework}
\label{sec:orge4889f4}

@@

\subsection*{Results}
\label{sec:org9e38ff3}

\subsubsection*{Summary statistics}
\label{sec:org12efa6c}

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Sun Apr  7 12:05:30 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & $275$ & $0.574$ & $  0.593$ & $  0.49$ & $0$ & $1$ \\ 
   & Gender - Female & $76$ & $0.159$ & $  0.169$ & $  0.37$ & $0$ & $1$ \\ 
   & Gender - Couple & $128$ & $0.267$ & $  0.238$ & $  0.43$ & $0$ & $1$ \\ 
   & Founder died & $58$ & $0.121$ & $  0.098$ & $  0.30$ & $0$ & $1$ \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & $178$ & $0.372$ & $  0.410$ & $  0.49$ & $0$ & $1$ \\ 
   & Self-Identification - Foundation & $101$ & $0.211$ & $  0.189$ & $  0.39$ & $0$ & $1$ \\ 
   & Self-Identification - Collection & $74$ & $0.154$ & $  0.140$ & $  0.35$ & $0$ & $1$ \\ 
   & Self-Identification - Other & $126$ & $0.263$ & $  0.261$ & $  0.44$ & $0$ & $1$ \\ 
   & Founder name in Museum name & $229$ & $0.478$ & $  0.488$ & $  0.50$ & $0$ & $1$ \\ 
   & MOW inclusion & $91$ & $0.190$ & $  0.304$ & $  0.46$ & $0$ & $1$ \\ 
   & AN Ranking - Not Included & $NA$ & $NA$ & $  0.797$ & $  0.40$ & $0$ & $1$ \\ 
   & AN Ranking - Included & $NA$ & $NA$ & $  0.150$ & $  0.36$ & $0$ & $1$ \\ 
   & AN Ranking - Dropped & $NA$ & $NA$ & $  0.054$ & $  0.23$ & $0$ & $1$ \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density (country) & $NA$ & $NA$ & $  0.411$ & $  1.23$ & $0.00077$ & $27.26$ \\ 
   & Pop. (millions) within 10km & $NA$ & $NA$ & $  1.322$ & $  1.69$ & $0.000087$ & $10.81$ \\ 
   & Pop. (millions) country & $NA$ & $NA$ & $156.197$ & $287.82$ & $0.037$ & $1412.36$ \\ 
   & Nbr PM within 10km & $NA$ & $NA$ & $  1.601$ & $  2.97$ & $0$ & $15$ \\ 
   & PM density (10km) & $NA$ & $NA$ & $  1.423$ & $  4.01$ & $0$ & $41.85$ \\ 
   & Europe and North America & $312$ & $0.651$ & $  0.645$ & $  0.48$ & $0$ & $1$ \\ 
   & Region - Africa & $7$ & $0.015$ & $  0.012$ & $  0.11$ & $0$ & $1$ \\ 
   & Region - Asia & $128$ & $0.267$ & $  0.282$ & $  0.45$ & $0$ & $1$ \\ 
   & Region - Europe & $241$ & $0.503$ & $  0.501$ & $  0.50$ & $0$ & $1$ \\ 
   & Region - Latin America & $22$ & $0.046$ & $  0.042$ & $  0.20$ & $0$ & $1$ \\ 
   & Region - North America & $71$ & $0.148$ & $  0.143$ & $  0.35$ & $0$ & $1$ \\ 
   & Region - Oceania & $10$ & $0.021$ & $  0.019$ & $  0.14$ & $0$ & $1$ \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

\subsubsection*{Hazard rate and Age Dependence}
\label{sec:org01e6edd}

\begin{figure}[htbp]
\centering
\includegraphics[width=16cm]{../figures/p_hazard.png}
\caption{\label{fig:p_hazard}Private Museum hazard function}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=14cm]{../figures/p_surv.png}
\caption{\label{fig:p_surv}Private Museum Survival probability}
\end{figure}

@@

\subsubsection*{Regression Results}
\label{sec:org4878b83}

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Sun Apr  7 15:01:01 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}ll}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4}\\ 
 \hline
  \multicolumn{3}{l}{\textbf{Founder}} \\ 
 & Gender - Female & $.22 \; (0.37)$ \\ 
   & Gender - Couple & $.14 \; (0.36)$ \\ 
   & Founder died & $.28 \; (0.53)$ \\ 
   \multicolumn{3}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & $.71 \; (0.48)$ \\ 
   & Self-Identification - Collection & $.14 \; (0.59)$ \\ 
   & Self-Identification - Other & $1.32 \; (0.38)^{***}$ \\ 
   & AN Ranking - Included & $.50 \; (0.38)$ \\ 
   & AN Ranking - Dropped & $.82 \; (0.52)$ \\ 
   & Founder name in Museum name & $-.35 \; (0.33)$ \\ 
   & MOW inclusion & $-.90 \; (0.40)^{*}$ \\ 
   \multicolumn{3}{l}{\textbf{Environment}} \\ 
 & PM density (country) & $.56 \; (0.42)$ \\ 
   & PM density$^{2}$ (country) & $-.02 \; (0.02)$ \\ 
   & Pop. (millions) within 10km & $.29 \; (0.11)^{**}$ \\ 
   & Nbr PM within 10km & $.30 \; (0.09)^{***}$ \\ 
   & Nbr PM (10km) * Pop (10km) & $-.10 \; (0.04)^{**}$ \\ 
   \hline
 & Museum-years & $6423$ \\ 
   & Closures & $52$ \\ 
   & log. Likelihood & $-253.41$ \\ 
   & AIC & $536.82$ \\ 
   & BIC & $566.09$ \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}

@@

\paragraph*{Control Variables}
\label{sec:org75141bd}

@@

\paragraph*{Identity Variables}
\label{sec:orge692d76}

@@

\paragraph*{Organizational transformation}
\label{sec:orge8aaa4f}

@@

\paragraph*{Competition}
\label{sec:orgd4359d4}
\begin{figure}[htbp]
\centering
\includegraphics[width=18cm]{../figures/p_pred_popprxcnt.png}
\caption{\label{fig:p_pred_popprxcnt}Predicted Avg. Hazard Rate on Regional PM Density and Population}
\end{figure}

@@

\subsection*{Conclusion}
\label{sec:org77289d2}
TBD

>>>>

% Created 2024-04-16 di 12:30
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

\setlength{\parindent}{1.2cm}
\author{Johannes }
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Johannes },
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 29.2 (Org mode 9.6.26)}, 
 pdflang={English}}
\begin{document}

\section*{Identity and the closure of private art museums}

\subsection*{Introduction}

@@

\subsection*{Private museums}

\subsection*{Theoretical framework}

@@

\subsubsection*{Identity and the survival prospects of non-profit organizations}

An identity that is legitimate (understandable) and favorable (positive) has been shown to have a vast number of positive outcomes for organizations \parencite{Lange_Lee_Dai_2010_reputation}.
As gaining the approval of different stakeholders is necessary for being understood and/or supported by other organizations in the environment, having a clearly defined and favorable identity influences resource acquisition and thereby survival prospects \parencite{Rao_1994_reputation}.
Even for non-profit organizations such as museums, which do not produce tangible goods (a domain where identity-related effects are present, e.g. \cite{Hsu_2015_granted,Bogaert_etal_2014_ecological}), a clear and positive identity might be helpful in a number of ways:
In particular in the context of private museums, decline of legitimacy or reputation could lead to lower visitor numbers, less discounts from art dealers, less government grants or lower chances on collaborations with other museums or corporations, resulting in lower revenues and higher acquisition costs.

@@

\subsubsection*{Organizational transformation}

\textcite{Carroll_Khessina_2019_demography} argue that transformation of core features of organizations such as changes in technology or authority can have divergent consequences. 
On the one hand, it can disrupt internal routines as well as external customer relations by decreasing (perceived) reliability and accountability as the change upsets established perceptions, which can lead to higher mortality. 
On the other hand, organizational transformation can be necessary to adapt to a changing environment, and hence be beneficial for survival.

@@

\subsubsection*{Competition}

@@

\subsubsection*{Other predictors of organizational survival}

\paragraph*{Age}

@@

\subsection*{Data and Methods}

\subsubsection*{Dependent Variable}

A newly constructed database, assembled from different sources,  is used to measure the survival of private museums (cf. \textcite{Velthuis_etal_2023_boom} for details).
First, existing databases of private art museums are harmonized.
Secondly, the online presences of 14 English art publications were exhaustively searched for any mention of private museums.
After identifying unique institutions, data on these organizations was collected such as opening year, closing year (of those which closed) and founder information.
Currently, the database includes 547 museums (of which 446 are currently open, the remainder having closed or transformed into other organizational forms).
Using this database allows to reconstruct the lifecourse of the each institution with the the unit of analysis as museum-year:
The main dependenent variable is thus an indicator of museum closure, which takes the value of 1 for the museums which close in the year of their closure, and 0 otherwise.
Typically for survival data, museums that do not close during the observation period are right-censored, i.e. for such museums the dependent variable is zero for all years.

\subsubsection*{Main Predictors}

\paragraph*{Legitimacy}

@@

\paragraph*{Reputation}

@@

\paragraph*{Organizational transformation}

A measure of founder death is constructed as a time-varying covariate, and is set to 1 for museum-years after the death of the founder.

\paragraph*{Competition}

On a national level, density of private museum is calculated as the number of private museums per million.
On a local level, I use the Global Human Settlement Layer \parencite{EC_2023_GHSL} to estimate the number of private museums and population counts inside a radius of ten kilometers around each private museum for each year.
To be able to estimate both competition and demand/audience/population separately, I do not calculate densities as per capita rates, but include the local museum counts, local population in millions as well as an interaction between the two.

\subsubsection*{Control variables}

@@

\subsubsection*{Analytical framework}

@@

\subsection*{Results}

\subsubsection*{Summary statistics}

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Mon Apr 15 11:30:07 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & 275 & 0.574 &   0.593 &   0.49 & 0 & 1 \\ 
   & Gender - Female & 76 & 0.159 &   0.169 &   0.37 & 0 & 1 \\ 
   & Gender - Couple & 128 & 0.267 &   0.238 &   0.43 & 0 & 1 \\ 
   & Founder died & 58 & 0.121 &   0.098 &   0.30 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & 178 & 0.372 &   0.410 &   0.49 & 0 & 1 \\ 
   & Self-Identification - Foundation & 101 & 0.211 &   0.189 &   0.39 & 0 & 1 \\ 
   & Self-Identification - Collection & 74 & 0.154 &   0.140 &   0.35 & 0 & 1 \\ 
   & Self-Identification - Other & 126 & 0.263 &   0.261 &   0.44 & 0 & 1 \\ 
   & Founder name in Museum name & 229 & 0.478 &   0.488 &   0.50 & 0 & 1 \\ 
   & MOW inclusion & 91 & 0.190 &   0.304 &   0.46 & 0 & 1 \\ 
   & AN Ranking - Not Included &  &  &   0.797 &   0.40 & 0 & 1 \\ 
   & AN Ranking - Included &  &  &   0.150 &   0.36 & 0 & 1 \\ 
   & AN Ranking - Dropped &  &  &   0.054 &   0.23 & 0 & 1 \\ 
   & PC1 (Size) & 76.0366391388584 & 0.159 &   0.138 &   1.88 & -6.4 & 2.62 \\ 
   & PC2 (Support) & 58.6628793020593 & 0.122 &   0.179 &   1.49 & -5 & 2.74 \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density (country) &  &  &   0.411 &   1.23 & 0.00077 & 27.26 \\ 
   & Pop. (millions) within 10km &  &  &   1.322 &   1.69 & 0.000087 & 10.81 \\ 
   & Pop. (millions) country &  &  & 156.197 & 287.82 & 0.037 & 1412.36 \\ 
   & Nbr PM within 10km &  &  &   1.601 &   2.97 & 0 & 15 \\ 
   & PM density (10km) &  &  &   1.423 &   4.01 & 0 & 41.85 \\ 
   & Europe and North America & 312 & 0.651 &   0.645 &   0.48 & 0 & 1 \\ 
   & Region - Africa & 7 & 0.015 &   0.012 &   0.11 & 0 & 1 \\ 
   & Region - Asia & 128 & 0.267 &   0.282 &   0.45 & 0 & 1 \\ 
   & Region - Europe & 241 & 0.503 &   0.501 &   0.50 & 0 & 1 \\ 
   & Region - Latin America & 22 & 0.046 &   0.042 &   0.20 & 0 & 1 \\ 
   & Region - North America & 71 & 0.148 &   0.143 &   0.35 & 0 & 1 \\ 
   & Region - Oceania & 10 & 0.021 &   0.019 &   0.14 & 0 & 1 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

\subsubsection*{Hazard rate and Age Dependence}

\begin{figure}[htbp]
\centering
\includegraphics[width=16cm]{../figures/p_hazard.pdf}
\caption{\label{fig:p_hazard}Private Museum hazard function}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=14cm]{../figures/p_surv.pdf}
\caption{\label{fig:p_surv}Private Museum Survival probability}
\end{figure}

@@

\subsubsection*{Regression Results}

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Mon Apr 15 11:32:02 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4}\\ 
 \hline
  \multicolumn{3}{l}{\textbf{Founder}} \\ 
 & Gender - Female & .22 \; (0.37) \\ 
   & Gender - Couple & .14 \; (0.36) \\ 
   & Founder died & .28 \; (0.53) \\ 
   \multicolumn{3}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .71 \; (0.48) \\ 
   & Self-Identification - Collection & .14 \; (0.59) \\ 
   & Self-Identification - Other & 1.32 \; (0.38)^{***} \\ 
   & AN Ranking - Included & .50 \; (0.38) \\ 
   & AN Ranking - Dropped & .82 \; (0.52) \\ 
   & Founder name in Museum name & -.35 \; (0.33) \\ 
   & MOW inclusion & -.90 \; (0.40)^{*} \\ 
   \multicolumn{3}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .56 \; (0.42) \\ 
   & PM density$^{2}$ (country) & -.02 \; (0.02) \\ 
   & Pop. (millions) within 10km & .29 \; (0.11)^{**} \\ 
   & Nbr PM within 10km & .30 \; (0.09)^{***} \\ 
   & Nbr PM (10km) * Pop (10km) & -.10 \; (0.04)^{**} \\ 
   \hline
 & Museum-years & 6423 \\ 
   & Closures & 52 \\ 
   & log. Likelihood & -253.41 \\ 
   & AIC & 536.82 \\ 
   & BIC & 566.09 \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}

@@

\paragraph*{Control Variables}

@@

\paragraph*{Identity Variables}

@@

\paragraph*{Organizational transformation}

@@

\paragraph*{Competition}

\begin{figure}[htbp]
\centering
\includegraphics[width=18cm]{../figures/p_pred_popprxcnt.pdf}
\caption{\label{fig:p_pred_popprxcnt}Predicted Avg. Hazard Rate on Regional PM Density and Population}
\end{figure}

@@

\subsection*{Conclusion}

TBD
